Additional analysis

### 2018-06-25 03_additional-analysis.Rmd
Use new color system

ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = c(ngo_red, ngo_blue), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```

@@

ggplot(coef_summary_charity, aes(x = fct_rev(give_charity_3), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "How often do you give to charity?", y = "Median amount donated") +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```

@@

ggplot(coef_summary_vol_relig, aes(x = fct_rev(volunteer), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = c(ngo_orange, ngo_green), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "Have you volunteered in the last 12 months?", y = "Median amount donated") +
  facet_wrap(~ religiosity_bin) +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```

@@

ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary_likely, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = c(ngo_red, ngo_blue), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```

>>>>

ggplot(coefs_posterior, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```

@@

ggplot(coef_summary_charity, aes(x = fct_rev(give_charity_3), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = ngo_cols("orange", "green", name = FALSE), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "How often do you give to charity?", y = "Median amount donated") +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```

@@

ggplot(coef_summary_vol_relig, aes(x = fct_rev(volunteer), y = estimate)) +
  geom_pointrange(aes(ymin = conf.low, ymax = conf.high, color = crackdown), 
                  position = position_dodge(width = 0.5)) +
  scale_color_manual(values = ngo_cols("orange", "green", name = FALSE), name = NULL) +
  scale_y_continuous(labels = dollar) +
  labs(x = "Have you volunteered in the last 12 months?", y = "Median amount donated") +
  facet_wrap(~ religiosity_bin) +
  theme_ngos() +
  theme(legend.position = "bottom",
        panel.grid.major.x = element_blank())
```

@@

ggplot(coefs_posterior_likely, aes(x = value, y = fct_rev(term_clean_fct))) +
  stat_density_ridges(aes(fill = model_name), alpha = 0.6, color = "black",
                      rel_min_height = 0.01, scale = 1.5, 
                      quantile_lines = TRUE, quantiles = 2) +
  geom_segment(data = coefs_summary_likely, 
               aes(x = conf.low, xend = conf.high, 
                   y = fct_rev(term_clean_fct), yend = fct_rev(term_clean_fct)),
               size = 1) +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) + 
  scale_fill_manual(values = ngo_cols("red", "blue", name = FALSE), name = NULL) +
  labs(x = "Posterior median estimate + 90% credible interval", y = NULL,
       caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0") +
  facet_wrap(~ full_model, scales = "free") + 
  theme_ngos() +
  theme(legend.position = "bottom",
        strip.text = element_blank())
```
